Computing Exact Restricted Isometry Constants via\\ Mixed Integer Semidefinite Programming

### 2016-03-14 RIP-MISDP-Paper/IEEE_RIP-MISDP.tex
removed the remark, since it is unneccessary

\begin{remark}\label{Rk1rmk}
  Theorem \ref{Rk1thm} still holds, if additional constraints involving
  only $z$-variables are added, e.g., fixing some $z_j$ to $0$ or $1$. In
  particular, \eqref{MISDP} or equivalently \eqref{Rk1MISDP} can be
  solved by branch and bound.
\end{remark}

Theorem~\ref{Rk1thm} and Remark~\ref{Rk1rmk} do not guarantee that any
found solution will have rank one. However, branch and bound will still
produce the correct optimal value. This suffices for our application of
computing the RIP constants $\alpha_k$ and $\beta_k$. For other
applications like SPCA, an extreme solution can be generated with an
algorithm proposed by Pataki~\cite{coneLP}.

>>>>

Theorem~\ref{Rk1thm} does not guarantee that any
found solution will have rank one, only that the optimal objective
values agree. This suffices for our application of
computing the RIP constants $\alpha_k$ and $\beta_k$. For other
applications like SPCA, an extreme solution can be generated with an
algorithm proposed by Pataki~\cite{coneLP}.
